A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-08 manuscript/main.tex
manuscript images
manuscript Wed  8 Jan 2025 16:55:43 EST

\usepackage{color}
\usepackage{dcolumn} % decimal align in tables
\usepackage{bm} % bold math
\usepackage{graphicx}
\usepackage{multirow} % for table cells to span rows
\usepackage{pifont} % for checkmarks
\usepackage{epsfig}
\usepackage{amsmath} % matrix
% \usepackage{subfigure}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{natbib}
\usepackage{gensymb}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11.0in}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{comment}
%for corrections
\usepackage[normalem]{ulem}
\usepackage{hyperref} % allows hyperlinking for references
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage{xcolor}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\usepackage{subcaption}
% \usepackage{titling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
The single-angle encoding (Fig. \ref{fig:A1}) is the simplest and takes the following form,
\begin{equation}
	U_{\text{A1}} = \prod_{i=0}^{n} R^{Y}_{i}(x_{i}),
	\label{eq:A1}
\end{equation}
where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
Like the single-angle encoding, the double-angle encoding (Fig. \ref{fig:A2}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
\begin{equation}
	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}).
	\label{eq:A2}
\end{equation}
The Mitarai encoding layer (Fig. \ref{fig:M}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
\begin{equation}
	U_{\text{M}}  = \prod_{i=0}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2})).
	\label{eq:M}
\end{equation}
Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:IQP}) is defined as,
\begin{equation}
	U_{\text{IQP}}  = \prod_{i=0}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij},
	\label{eq:IQP}
\end{equation}
where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A1.png}
		\caption{}
		\label{fig:A1}		
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A2.png}
		\caption{}
		\label{fig:A2}		
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=1\columnwidth]{images/encoders/quantikz/M.png}
		\caption{}
		\label{fig:M}		
	\end{subfigure}%	  
	\hfill
	\begin{subfigure}{1\textwidth}
		\centering
		    \includegraphics[width=\columnwidth]{images/encoders/quantikz/IQP.png}
		\caption{}
		\label{fig:IQP}
	\end{subfigure}%
	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
	\label{fig:encoders}
\end{figure}

@@

Following the encoding layers,variational (or ansatz) layers are used to introduce trainable parameters into the quantum circuit.
We use a mixed notation from Refs. \citep{suzuki_predicting_2020} and \citep{sim_expressibility_2019}, since Ref. \citep{sim_expressibility_2019} contains all of the variational layers used within this work.
We relegate the discussion of the expressibility and entanglement of these layers to Section \ref{section:results_and_discussion}

\begin{equation}
	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}
	\label{eq:general_variational}
\end{equation}

12 variational layers
ESU2
Efficient-CRX
Efficient-CRZ
Full-CRX
Full-CRZ
Full-Pauli-CRX
Full-Pauli-CRZ
HWE-CNOT
HWE-CZ
Hadamard
Modified-Pauli-CRX
Modified-Pauli-CRZ

\begin{quantikz}
	\lstick{$q_0$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{0}^{2}))} & \gate{R_{Z} (\arccos(x_{0})^{2})} & \\
	\lstick{$q_1$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{1}^{2}))} & \gate{R_{Z} (\arccos(x_{1})^{2})} & \\
	\lstick{$q_2$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{2}^{2}))} & \gate{R_{Z} (\arccos(x_{2})^{2})} & \\
	\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots & \\
	\lstick{$q_n$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{n}^{2}))} & \gate{R_{Z} (\arccos(x_{n})^{2})} & \\
\end{quantikz}

\begin{equation}
	U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}   \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n}
\end{equation}

$v \in \{1, 3, 5\}$
$k \in \{1, 3, 5\}$

\subsection{Implementation}
Our work was implemented in Python using PennyLane for constructing the quantum circuits, and Qulacs as a primary backend for simulating the circuits. The optimization was implemented using the scipy.optimize module from the SciPy library. Classical models were implemented using scikit-learn while processing of the data was handled with Pandas, NumPy, and SciPy libraries.

Simulated using FakeQuebecbackend

@@

For the function fitting dataset, there is only one feature per target value.
For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}

@@

>>>>

\usepackage{color}
\usepackage{dcolumn} % decimal align in tables
\usepackage{bm} % bold math
\usepackage{graphicx}
\usepackage{multirow} % for table cells to span rows
\usepackage{pifont} % for checkmarks
\usepackage{epsfig}
\usepackage{amsmath} % matrix
% \usepackage{subfigure}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{natbib}
\usepackage{gensymb}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11.0in}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{comment}
%for corrections
\usepackage[normalem]{ulem}
\usepackage[hidelinks]{hyperref} % allows hyperlinking for references
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage{xcolor}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\usepackage{subcaption}
% \usepackage{titling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
The single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}) is the simplest and takes the following form,
\begin{equation}
	U_{\text{A1}} = \prod_{i=0}^{n} R^{Y}_{i}(x_{i}),
	\label{eq:A1}
\end{equation}
where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
Like the single-angle encoding, the double-angle encoding (Fig. \ref{fig:encoders} \textbf{(b)}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
\begin{equation}
	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}).
	\label{eq:A2}
\end{equation}
The Mitarai encoding layer (Fig. \ref{fig:encoders} \textbf{(c)}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
\begin{equation}
	U_{\text{M}}  = \prod_{i=0}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2})).
	\label{eq:M}
\end{equation}
Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:encoders} \textbf{(d)}) is defined as,
\begin{equation}
	U_{\text{IQP}}  = \prod_{i=0}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij},
	\label{eq:IQP}
\end{equation}
where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.

%\begin{figure}[H]
%       \centering
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A1.png}
	%               \caption{}
	%               \label{fig:A1}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A2.png}
	%               \caption{}
	%               \label{fig:A2}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=1\textwidth]{images/encoders/quantikz/M.png}
	%               \caption{}
	%               \label{fig:M}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{1\textwidth}
	%               \centering
	%                   \includegraphics[width=\textwidth]{images/encoders/quantikz/IQP.png}
	%               \caption{}
	%               \label{fig:IQP}
	%       \end{subfigure}%
%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
%       \label{fig:encoders}
%\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/encoders/quantikz/combined.png}
	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
	\label{fig:encoders}
\end{figure}

@@

Following the encoding layers,variational (or ansatz) layers are used to introduce trainable parameters into the quantum circuit.
We use a mixed notation from Refs. \citep{suzuki_predicting_2020} and \citep{sim_expressibility_2019}, since Ref. \citep{sim_expressibility_2019} contains all of the variational layers used within this work.
We relegate the discussion of the expressibility and entanglement examined in that work to Section \ref{section:results_and_discussion}.
A general variational layer can be denoted as,
\begin{equation}
	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}), % E_{\text{ent}}^{v}
	\label{eq:general_variational}
\end{equation}
where $\bm{\theta}$ denotes the variational parameters and $v$ denotes the number of times that the layer is repeated within the circuit. 
As $v$ increases and the number of trainable parameters ($\bm{\theta}$) increase, the theoretical assumption is that the model expressibility should also increase.
In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
We examine 12 different variational circuits, as shown in Fig. \ref{fig:ansatz}, which are denoted using the following labels: Modified-Pauli-CRZ (Fig. \ref{fig:ansatz}\textbf{(a)}) , Modified-Pauli-CRX (Fig. \ref{fig:ansatz}\textbf{(b)}), Efficient-CRZ (Fig. \ref{fig:ansatz}\textbf{(c)}), Efficient-CRX (Fig. \ref{fig:ansatz}\textbf{(d)}),, HWE-CNOT (Fig. \ref{fig:ansatz}\textbf{(e)}), HWE-CZ (Fig. \ref{fig:ansatz}\textbf{(f)}), ESU2 (Fig. \ref{fig:ansatz}\textbf{(g)}), Full-Pauli-CRZ (Fig. \ref{fig:ansatz}\textbf{(h)}), Full-Pauli-CRX (Fig. \ref{fig:ansatz}\textbf{(i)}), Hadamard (Fig. \ref{fig:ansatz}\textbf{(j)}), Full-CRZ (Fig. \ref{fig:ansatz}\textbf{(k)}), and Full-CRX (Fig. \ref{fig:ansatz}\textbf{(l)}),

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/ansatz/quantikz/combined.png}
	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
	\label{fig:ansatz}
\end{figure}

Now that we have define the encoding (Eq. \ref{eq:general_encoding}) and variational (Eq. \ref{eq:general_variational}) circuits, we can then combine them to denote a general, complete circuit as,
\begin{equation}
	\ket{\Psi} = U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n},
\end{equation}
where we choose $k \in \{1, 3, 5\}$, which denotes the re-upload depth (RUD) of the circuit.
When a sufficient number of data re-uploading occur, it has been shown by P\'{e}rez-Salinas \textit{et al.} that data re-uploading is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}

Lastly, to recover the predicted target values, $\hat{y}_{i}$, from our quantum circuits, measurement of the quantum state, $\ket{\Psi}$, must be performed.
To perform this operation, we apply the Pauli Z operator on the first qubit denoted as,
\begin{equation}
	\hat{y}_{i} = \bra{\Psi}Z_{0}\ket{\Psi}_{i}.
	\label{eq:y_pred}
\end{equation}
The set of predicted target values, $\bm{\hat{y}} = (\hat{y}_{1}, \ldots, \hat{y}_{N}) \in \mathbb{R}^{N}$, where $N$ is the number of samples, is then passed to the loss function, $\mathcal{L}(\bm{y}, \bm{\hat y})$, where $y_{i}$ belongs to the set of true target values $\bm{y} = (y_{1}, \ldots, y_{N}) \in \mathbb{R}^{N}$.
In practice, $\mathcal{L}$ can be any loss function but we choose to use the mean square error loss function denoted as,
\begin{equation}
	\mathcal{L}(\bm{y}, \bm{\hat y}) = \frac{1}{N} \sum_{i=1}^{N} (y_{i} - \hat{y}_{i})^{2}.
	\label{eq:isthisloss}
\end{equation}

\subsection{Implementation}
Python
Pennylane
Pennylane Qiskit
Pennylane Qulacs
Qiskit
SciPy
Scikit-learn

Simulated using FakeQuebecbackend
IBM Quebec

Error mitigation using
MITIQ (delete because this is useless for the Qiskit stuff... try level 2 for ZNE...)

@@

For the function fitting dataset, there is only one feature per target value.

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../classical_testing/BSE/BSE_16_learning_curve}
		\caption{}
		\label{fig:bse16learningcurve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
		\caption{}
		\label{fig:classicalfuncfit}
	\end{subfigure}
	\caption{}
	\label{fig:bse16classical}	
\end{figure}

For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}

@@

\subsection{Classical Data Analysis}

 \begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/BSE/classical_features_MAE.png}
		\caption{}
		\label{fig:BSE_bse_classical_features_MAE}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/BSE/classical_features_R2.png}
		\caption{}
		\label{fig:BSE_classical_features_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/DDCC/DDCC_feature_set.png}
		\caption{}
		\label{fig:DDCC_feature_set}
	\end{subfigure}
	\hfill	
	\caption{}
	\label{fig:chemical_classical_features}
\end{figure}

\subsection{Function Fitting}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_heatplots.png}
		\caption{}
		\label{fig:linear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_boxplots.png}
		\caption{}
		\label{fig:linear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_heatplots.png}
		\caption{}
		\label{fig:quadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_boxplots.png}
		\caption{}
		\label{fig:quadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_heatplots.png}
		\caption{}
		\label{fig:sine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_boxplots.png}
		\caption{}
		\label{fig:sine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:fivequbit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_heatplots.png}
		\caption{}
		\label{fig:sixteenlinear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_boxplots.png}
		\caption{}
		\label{fig:sixteenlinear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
		\caption{}
		\label{fig:sixteenquadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
		\caption{}
		\label{fig:sixteenquadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_heatplots.png}
		\caption{}
		\label{fig:sixteensine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_boxplots.png}
		\caption{}
		\label{fig:sixteensine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:sixteensixteenqubit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubit_Linear_RUD_AL}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_circuitdepth_vs_R2}
		\caption{}
		\label{fig:linear_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
		\caption{}
		\label{fig:16qubit_Quadratic_RUD_AL}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_circuitdepth_vs_R2}
		\caption{}
		\label{fig:quadratic_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubitlinearrudal}
	\end{subfigure}	
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_circuitdepth_vs_R2}
		\caption{}
		\label{fig:sine_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:16qubit_RUD_AL}	
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_learning_curves.png}
		\caption{}
		\label{fig:linear_learning_curves}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_learning_curves.png}
		\caption{}
		\label{fig:quadratic_learning_curves}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_learning_curves.png}
		\caption{}
		\label{fig:sine_learning_curves}
	\end{subfigure}	
	\caption{}
	\label{fig:functionfitting_learning_curves}	
\end{figure}

\subsection{BSE}

\subsection{DDCC}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/DDCC_heatplots}
		\caption{}
		\label{fig:ddccheatplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/DDCC_boxplots}
		\caption{}
		\label{fig:ddccboxplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
		\caption{}
		\label{fig:allddcc5circuitdepthr2vsiterationtime}
	\end{subfigure}	
	\caption{}
	\label{fig:ddcc_all_analysis}	
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/DDCC/DDCC_RUDAL}
	\caption{}
	\label{fig:ddccrudal}
\end{figure}
